decompr: trade flow decomposition for Global Value Chain analysis

### 2015-01-02 README.Rmd
update to remove notice
small fixes

```{r load-package, echo=FALSE}
library(decompr)
```

@@

We can now decompose the elements using the Source decomposition.
```{r leontief}
lt <- leontief( elements )
```

@@

```{r source-eval}
dim(lt)
dim(lt2)
```

Wang Wei Zhu decomposition
------------------------------
We can now decompose the elements using the Wang-Wei-Zhu (or source) decomposition.
```{r wwz}
w <- wwz( elements )
```

@@

```{r wwz-eval}
str(w)
```

>>>>

```{r load-package, echo=FALSE, message=FALSE}
library(decompr)
```

@@

We can now decompose the elements using the Leontief decomposition.
```{r leontief}
lt <- leontief( elements )
```

@@

```{r source-eval}
dim(lt )
dim(lt2)
```

Wang Wei Zhu decomposition
------------------------------
We can now decompose the elements using the Wang-Wei-Zhu decomposition.

```{r wwz}
w <- wwz( elements )
```

@@

```{r wwz-eval}
str(w )
str(w2)
```
